Untitled

### 2019-05-28 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

>>>>

*Methodological consistency* The data in ForC is derived from a range of studies, often employing different methods. For this reason, criteria were introduced to standardise for differences in methodology. Where data was based on forest plot census measurements, studies which uses a minimum dbh measure of 10cm or greater were excluded from analysis.  
Estimates of total ecosystem primary productivity are based on measurements of the component parts of forest productivity. Since the components included in productivity estimates vary between studies, estimates of productivity were classified within the ForC database according to their components, and then filtered for analysis. Estimates of NPP were selected if they included foliage, branch, stem, coarse root, fine root and understory. Measures of NPP which included additional components were excluded. Estimates of ANPP were selected if they included foliage, stem growth and branch turnover. Any measures of primary productivity where components were unknown were excluded from analysis.
